Capstone Movielens Report

### 2025-11-14 reports/capstone-movielens.site/02-0.methods.Rmd
OMR, UE, UME models: review.

As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout the project:

@@

  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross-Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].

>>>>

As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *This Project*:

@@

  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the *K-Fold Cross-Validation* in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].

### 2025-11-14 reports/capstone-movielens.site/02-3.OMR-model.Rmd
OMR, UE, UME models: review.

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

::: {.noteblock data-latex=""}
To print the log, we use the custom function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) custom functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::

>>>>

::: {.noteblock data-latex=""}
In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

::: {.noteblock data-latex=""}
To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
:::

@@

::: {.noteblock data-latex=""}
To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::

### 2025-11-14 reports/capstone-movielens.site/02.4.UE-model.Rmd
OMR, UE, UME models: review.

::: {.noteblock data-latex=""}
The complete source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) script on _GitHub_.

:::

>>>>

::: {.noteblock data-latex=""}
To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::
